An institutional approach to attention allocation and venture resource mobilization and acquisition

### 2021-03-15 Manuscript.Rmd
Final manuscript for capstone submission - more to come later

authornote: |
  Lundquist College of Business

  Department of Management

@@

```{r fig.height=5, fig.width=8}
#Distribution of attention

@@

a  %>%
  ggplot(aes(Score)) +
  geom_bar() +
  facet_grid(~Attention) +
  theme_bw()+
  ylab("")+
  xlab("Attention score")

@@

a  %>%
  ggplot(aes(Score)) +
  geom_bar() +
  facet_grid(vars(`Income group`), vars(Attention)) +
  theme_bw() +
  ylab("")+
  xlab("Attention score")

@@

filter(b, Attention == "Network")  %>%
  ggplot(aes(Score, `Total Equity Sources`)) +
  geom_point()  +
  facet_grid(~`Income group`)+
  xlab("Attention to Network")+
  theme_bw()

filter(b, Attention == "Direct Funding")  %>%
  ggplot(aes(Score, `Capital Raised`)) +
  geom_point()  +
  facet_grid(~`Income group`)+
  xlab("Attention to Direct Funding")+
  theme_bw()

@@

>>>>

authornote: |
  Lundquist College of Business 
  Department of Management

@@

```{r fig.height=7, fig.width=9}
#Distribution of attention

@@

a  %>%
  ggplot(aes(Score)) +
  geom_bar() +
  facet_grid(~Attention) +
  theme_bw()+
  ylab("")+
  xlab("Attention score")+
  labs(title =  "Distribution of venture attention to resources by type of resource")

@@

a  %>%
  ggplot(aes(Score)) +
  geom_bar() +
  facet_grid(vars(`Income group`), vars(Attention)) +
  theme_bw() +
  ylab("")+
  xlab("Attention score")+
  labs(title =  "Distribution of venture attention to resources by type of resource and country classification")

@@

#Function to wrap long titles 
wrapper <- function(x, ...) 
{
  paste(strwrap(x, ...), collapse = "\n")
}

filter(b, Attention == "Network")  %>%
  ggplot(aes(Score, `Total Equity Sources`)) +
  geom_point()  +
  facet_grid(~`Income group`)+
  xlab("Attention to Network")+
  ggtitle(wrapper("Correlation between the venture network and the venture attention level to network by country classification", width = 80))+
  theme_bw()

filter(b, Attention == "Direct Funding")  %>%
  ggplot(aes(Score, `Capital Raised`)) +
  geom_point()  +
  facet_grid(~`Income group`)+
  xlab("Attention to Direct Funding")+
  ggtitle(wrapper("Correlation between  the venture’s total capital raised and the its attention level to direct funding by country classification", width = 80))+
  theme_bw()

@@

# Conclusion
